\documentclass[11pt, letterpaper, colorlinks=true]{moderncv}
\usepackage[utf8]{inputenc}
\moderncvtheme[black]{classic}
\usepackage[scale=0.85]{geometry}
\definecolor{linkblue}{HTML}{247BA0}
\AtBeginDocument{\hypersetup{urlcolor=linkblue,linkcolor=linkblue}}
\renewcommand*{\namefont}{\fontsize{30}{32}\mdseries\upshape}
\linespread{1.035}

\firstname{Sam}
\familyname{Schlesinger}
\mobile{+1~(508)~246~8980}
\email{sgschlesinger@gmail.com}
\homepage{SamuelSchlesinger.github.io}
\social[github]{SamuelSchlesinger}

\begin{document}

\makecvtitle
\vspace{-1em}

\section{Professional Experience}

\cventry{2022--Present}{Senior Software Engineer}{Google Chrome AI Security}{}{}
{
    \begin{itemize}
        \item Implemented a private zero-knowledge banking protocol.
        \item Co-authored the \href{https://github.com/cathieyun/draft-athm}{Anonymous Tokens with Hidden Metadata standards drafts} and \href{https://github.com/google/anonymous-tokens}{Rust implementation}; deployed to protect billions of users from spam texts via RCS/iMessage integration.
        \item Designed and implemented the \href{https://github.com/explainers-by-googlers/private-verification-tokens}{Private Verification Tokens API} in Chromium using ATHM to transfer low-entropy trust from regular to private browsing, reducing CAPTCHA friction while preserving privacy.
        \item Co-authored the \href{https://github.com/SamuelSchlesinger/draft-act}{Anonymous Credit Tokens (ACT) standards drafts} and \href{https://github.com/SamuelSchlesinger/anonymous-credit-tokens}{Rust implementation} for privacy-preserving API credits; presented ACT to the IETF Privacy Pass Working Group at IETF 123, IETF 124, and its May 2026 interim.
        \item Led a three-day cross-browser PACT workshop producing three \href{https://github.com/Moderation-of-unLinkable-Endorsements/internet-drafts}{Moderation of unLinkable Endorsements (MoLE) Internet-Drafts}; built an end-to-end Chromium prototype; presented at IETF 126. BoF expected at IETF 127 in San Francisco.
        \item Designed the \href{https://explainers-by-googlers.github.io/private-proof/}{Private Proof API} for anti-fraud in a post-third-party-cookie web. Led three engineers to implement in Chrome. Drafted novel \href{https://github.com/samuelSchlesinger/authenticated-pseudonyms/}{anonymous credential primitives}.
        \item Co-chair of W3C Anti-Fraud Community Group.
    \end{itemize}
}

\cventry{2022}{Software Engineer / Scientist}{Casper Labs}{}{}
{
    \begin{itemize}
        \item Co-designed novel \href{https://arxiv.org/abs/2205.06314}{consensus algorithm} (presented at FOCODILE 2022). Implemented in \href{https://github.com/casper-network/casper-node}{Casper node}, deployed in 2.0 upgrade.
        \item Researched zero-knowledge use cases and proposed network optimizations.
        \item Consulted C-suite on network security and scalability strategy.
    \end{itemize}
}

\cventry{2019--2022}{Software Engineer (Team Lead)}{SimSpace}{}{}
{
    \begin{itemize}
        \item Designed and implemented Attack Designer program.
        \item Designed consensus-lite protocol for multi-datacenter cluster coordination.
        \item Backend security lead: identified and fixed cryptographic vulnerabilities.
    \end{itemize}
}

\section{Community \& Outreach}

\cvitem{Creator}{\href{https://www.youtube.com/@computablesecrets}{Computable Secrets}, a YouTube channel explaining cryptography, formal methods, and \mbox{theoretical} computer science.}
\cvitem{Reviewer}{\href{https://www.cslib.io/}{CSLib}, reviewing formalized computer science contributions to its Lean library.}
\cvitem{Instructor}{Delivered tailored computer science lectures at local high schools and taught \href{https://codenext.withgoogle.com/}{Google Code Next} classes to high school students.}

\section{Skills}
\cvitem{Core}{Cryptography, Security, Distributed Systems, Internet Standards}
\cvitem{Engineering}{Rust, Haskell, TypeScript/JavaScript, Web Servers, PostgreSQL, Kubernetes, Smart Contracts}

\section{Education}
\cventry{2019}{B.A. Computer Science and Math}{UMass}{Amherst}{}{}

\end{document}
